---
title: "Hello, its me"
author: "Emily and Stephanie"
date: "3/7/2018"
output: 
  html_document:
    code_folding: hide
---

This chunck loads the tidyverse:
```{r message=FALSE}
library(tidyverse)
```

[LINK TO MINI-PROJECT 2 DESCRIPTION](https://beanumber.github.io/sds192/mod_data.html)

This chunck loads all the files available for the project through 
```{r}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```


Current Plan:

Design a function to see which top ~5 commities contributed, how much they contributed, and which party the commitie is affiliated with.  Then graph this information in the best way possible.  Then use a facet to graph multiple politians at one time on the same figure.  


Things To Use for Points:

* 2 of the 5 basic words (select(),  mutate(), etc)
* Using a Join 
* If we use a function for this, there is a bonus point involved.  If we start with a function design from the begining, this point will be easier 

Starting to write a function designed to give a tbl for the top 5 committees
```{r}

TopFive<-function(name_arg){
  candidates %>%
  filter(can_name==name_arg)
  
}
```
I think the general plan could be (sorry for spelling errors):

I think Joining Candidates and contributions by Cand_ID is a good plan 

Candidate name = Candidate ID  %>%
Donations for the Candidates from Conrtibutions using Candidate ID  %>%
Referencing back to commitiees data set for the name for committee ID = Commitee name %>%
Sorting descending popularity %>%
head(5)

Generic Plotting Plan:
$ = y-axis
committee = x-axis 
Color of Bars = Political Party 






