---
title: "Mini-Project-2"
author: "Emily and Stephanie"
date: "3/22/2018"
output:
  html_document:
    code_folding: hide
---

This chunk loads the tidyverse:

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggthemes)
```

[LINK TO MINI-PROJECT 2 DESCRIPTION](https://beanumber.github.io/sds192/mod_data.html)

This chunk loads all the files available for the project through:
```{r message=FALSE, warning=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

We decided to explore the connection between candidates and committee party affiliation and contribution.  We used the datasets candidates, committees and contributions to explore this relationship.  Additionally, we used GitHub to work over break.[^1]

We designed a function to see which top 5 committees contributed to a specific candidate and how much money was contributed.  Intiallt the graphic was going to 
display the committee party affiliation, however most committees did not have party ties so we decided to exclude this information in our final graphs. Detailed below is the path we took to develop the function.  

First, we chose which columns we wanted to work with from the candidate’s dataset.  Then we decided to explore Nancy Pelosi's connection with committees, so we filtered out for Nancy Pelosi.   

```{r message=FALSE, warning=FALSE}
NancyPelosi <- candidates %>%
  select(cand_id, cand_name, cand_party_affiliation) %>%
  filter(cand_name == 'PELOSI, NANCY')
```

Then we created a new dataset by joining Nancy Pelosi and contributions by using the left_join function.

```{r message=FALSE, warning=FALSE}
cand_contr <- left_join(NancyPelosi, contributions)
```

We next combined the candidates and contributions dataset we created with committees and selected the following columns: candidate ID, candidate name, candidate party affiliation, name, transaction amount and committee party affiliation.  Then we created a new column that was the sum of all transactions and used the distinct() function to remove redundancies in the rows.  We then arranged them in descending order by sum and took the top 5 observations. This was done in order to obtain a table that had the highest contributing committees for Nancy Pelosi.

```{r message=FALSE, warning=FALSE}
cand_contr_comm <- left_join(cand_contr, committees) %>%
  select(cand_id, cand_name, cand_party_affiliation, name, transaction_amt, cmte_party_affiliation) %>%
  group_by(name) %>%
  mutate(sum = sum(transaction_amt)) %>%
  select(cand_id, cand_name, cand_party_affiliation, name, cmte_party_affiliation, sum) %>%
  distinct(sum,cand_id, cand_name, cand_party_affiliation, name, cmte_party_affiliation) %>%
  arrange(desc(sum)) %>%
  head(5)
```

```{r message=FALSE, warning=FALSE}
ggplot(cand_contr_comm, aes(x=name, y=sum))+
  geom_histogram(stat="identity") + 
  labs(y="Dollars Contributed", x="Committee Name", title="Committee Contribution to Nancy Pelosi")+
  theme_minimal()+
  theme(axis.title.x = element_text(size=10),
        axis.text.x  = element_text(angle=90, vjust=0.5, size=10))

```

We used ggplot to create a bar graph of the top 5 committees that contributed funds to Nancy Pelosi. The bars ideally would have been color-coded by party affiliation; however the top 5 committees were committees that fundraised exclusively for Nancy Pelosi.  An issue we had here, was that the top 2 committees for Nancy Pelosi had the same name, so R stacked them in the same bar. Overall, this was not very interesting, so we created a function in order to look at other candidates quickly without repeating all the code.



In the next code chunk, we made a large table that joined the data by candidates.

```{r message=FALSE, warning=FALSE}
cand_contr_start <- candidates %>%
  select(cand_id,cand_name, cand_party_affiliation)
```


```{r message=FALSE, warning=FALSE}
cand_contrULTRA <- left_join(cand_contr_start, contributions) 
```

Then, we created a master list with all candidates, candidate ID, candidates party affiliation, name of each donation, donation amount, and the type of organization each donation is from. This table was then manipulated to contain the amount contributed by each committee.  Row redundancies were eliminated with the distinct () command.  

```{r message=FALSE, warning=FALSE}
cand_cantrULTRA2 <- left_join(cand_contrULTRA, committees) %>%
  select(cand_id, cand_name, cand_party_affiliation, name, transaction_amt, entity_type, cmte_party_affiliation) %>%
  group_by(name) %>%
  mutate(sum = sum(transaction_amt)) %>%
  select(cand_id, cand_name, cand_party_affiliation, name, cmte_party_affiliation, sum) %>%
  distinct(sum,cand_id, cand_name, cand_party_affiliation, name, cmte_party_affiliation) 
```

The function below makes the desired graph for any candidate.  Choosing any candidate and running it through the function “top_5” produces a graphic that shows the top 5 contributing committees.

```{r message=FALSE, warning=FALSE}
top_5 <- function(name_arg) {
  plot_data <- cand_cantrULTRA2 %>%
    filter(cand_name == name_arg) %>%
    arrange(desc(sum)) %>%
    head(5)
  ggplot(plot_data,  aes(x=name, y=sum))+
    geom_histogram(stat="identity")+
    labs(y="Dollars Contributed", x="Committee Name", title=name_arg)+
    theme_minimal()+
    theme(axis.title.x = element_text( size=10),
          axis.text.x  = element_text(angle=90, vjust=0.5, size=10))
}
```


In the next chunk we selected Jeff Denham, a random republican contained within the data set, and ran the name though the function "top_5"
```{r message=FALSE, warning=FALSE}
ROBY <- top_5( "DENHAM, JEFF")
ROBY
```


We noticed after running the function a few times that a lot of committees are not affiliated with a party.  This results in all of the bars being coded the same color, for NA. Overal it appears that most committees do not have a party affiliation. This interesting because we know that they back a specific candidate that is affiliated with a political party, indicating the committees should have a party affiliation. 


####Word Counter:
```{r}
wordcountaddin::text_stats("Exersize_3.Rmd")
```

[^1]: [This is the link to the github repository](https://github.com/EmilyGrote/sds192-mp2.git)


